04_DESeq_sexes

### 2019-05-28 analysis/04_DESeq2_sexes.Rmd
new order

a.colData$treatment <- factor(a.colData$treatment, levels = 
                             c("control", "bldg", "lay",
                               "inc.d3", "m.inc.d3", 
                               "inc.d9", "m.inc.d8", "m.inc.d9",
                               "inc.d17", "m.inc.d17",
                               "hatch",  "m.n2"  ,
                               "n5", "prolong", "extend", "n9" ))

@@

```{r returntotalDEGs, eval = T}
#DEGs.female_hypothalamus <- returntotalDEGs(dds.female_hypothalamus)
#DEGs.female_pituitary <- returntotalDEGs(dds.female_pituitary)
#DEGs.female_gonad <- returntotalDEGs(dds.female_gonad)
#DEGs.male_hypothalamus <- returntotalDEGs(dds.male_hypothalamus)
DEGs.male_pituitary <- returntotalDEGs(dds.male_pituitary)
#DEGs.male_gondad <- returntotalDEGs(dds.male_gondad)
```

```{r plotDEGs, eval = T}
#a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
#b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
#c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
#d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary")
#f <- plottotalDEGs(DEGs.male_gondad, "male gonad")
```

```{r plottotalDEGs, eval = T}
plot_grid(#a + theme(legend.position = "none"),
          #b + theme(legend.position = "none"),
          #c + theme(legend.position = "none"),
          #d + theme(legend.position = "none"),
          e + theme(legend.position = "none"),
          #f + theme(legend.position = "none"),
          nrow = 2) 
```

@@

```{r plotpca, fig.dim = c(12, 10), eval=T}
p1 <- plotPCAs(pcas.female_hypothalamus, "female hypothalamus") 
p2 <- plotPCAs(pcas.female_pituitary, "female pituitary")   
p3 <- plotPCAs(pcas.female_gonad, "female gonad") 
p4 <- plotPCAs(pcas.male_hypothalamus, "male hypothalamus") 
p5 <- plotPCAs(pcas.male_pituitary, "male pituitary") 
p6 <- plotPCAs(pcas.male_gondad, "male gonad") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels

@@

allPC1s <- plot_grid(p1 + theme_noaxislabels + ylim(c(-40,40)), 
                     p4 + theme_noaxislabels + ylim(c(-40,40)), 
                     p2 + theme_noaxislabels + ylim(c(-40,40)),
                     p5 + theme_noaxislabels + ylim(c(-40,40)),
                     p3 + theme_nolegend + ylim(c(-40,40)) ,
                     p6 + theme_nolegend + ylim(c(-40,40)) ,
                     ncol = 2)

@@

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 10)
plot(pc1)
dev.off()

>>>>

a.colData$treatment <- factor(a.colData$treatment, levels = 
                             c("control", "bldg", "lay",
                               "inc.d3", "inc.d9", "inc.d17",
                               "hatch", "n5", "n9",

                               "m.inc.d3", "m.inc.d8", "m.inc.d9",
                               "m.inc.d17",  "m.n2"  ,
                                "prolong", "extend" ))

@@

```{r returntotalDEGs, eval = T}
DEGs.female_hypothalamus <- returntotalDEGs(dds.female_hypothalamus)
DEGs.female_pituitary <- returntotalDEGs(dds.female_pituitary)
DEGs.female_gonad <- returntotalDEGs(dds.female_gonad)
DEGs.male_hypothalamus <- returntotalDEGs(dds.male_hypothalamus)
DEGs.male_pituitary <- returntotalDEGs(dds.male_pituitary)
DEGs.male_gondad <- returntotalDEGs(dds.male_gondad)

```{r plottotalDEGs, eval = T}
a <- plottotalDEGs(DEGs.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(DEGs.female_pituitary, "female pituitary")
c <- plottotalDEGs(DEGs.female_gonad, "female gonad")
d <- plottotalDEGs(DEGs.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(DEGs.male_pituitary, "male pituitary")
f <- plottotalDEGs(DEGs.male_gondad, "male gonad")

myDEGs <- plot_grid(a + theme_noaxislabels,
          d + theme_noaxislabels,
          b + theme_noaxislabels,
          e + theme_noaxislabels,
          c + theme_nolegend,
          f + theme_nolegend,
          nrow = 3) 
myDEGs

pdf("../figures/sexes/plottotalDEGs-1.pdf", width = 12, height = 10)
plot(myDEGs)
dev.off()
```

@@

```{r plotpca, eval=T}
p1 <- plotPCAs(pcas.female_hypothalamus, "female hypothalamus") 
p2 <- plotPCAs(pcas.female_pituitary, "female pituitary")   
p3 <- plotPCAs(pcas.female_gonad, "female gonad") 
p4 <- plotPCAs(pcas.male_hypothalamus, "male hypothalamus") 
p5 <- plotPCAs(pcas.male_pituitary, "male pituitary") 
p6 <- plotPCAs(pcas.male_gondad, "male gonad") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels

@@

allPC1s <- plot_grid(p1 + theme_noaxislabels + ylim(c(-35,35)), 
                     p4 + theme_noaxislabels + ylim(c(-35,35)), 
                     p2 + theme_noaxislabels + ylim(c(-35,35)),
                     p5 + theme_noaxislabels + ylim(c(-35,35)),
                     p3 + theme_nolegend + ylim(c(-35,35)) ,
                     p6 + theme_nolegend + ylim(c(-35,35)) ,
                     ncol = 2)

@@

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 10)
plot(pc1)
dev.off()
```
